---
title: "131_HW3"
output: github_document
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache.extra = rand_seed)
```

```{r, message=FALSE}
library(tidyverse)
library(tidymodels)
titanic <- read_csv("/Users/zackreardon/Downloads/homework-3/data/titanic.csv")
```

Question 1.

```{r}
set.seed(100)

titanic_split <- initial_split(titanic, prop = 0.70, strata = survived)

titanic_train <- training(titanic_split)
titanic_test <- testing(titanic_split)

tr <- nrow(titanic_train) # determine number of observations
tt <- nrow(titanic_test) # determine number of observations

print(tr/(tr+tt))

titanic_train # look at training data
```
There appears to be some missing data regarding the age of some passengers as well as the cabin number. It is a good idea to use stratified sampling for this data since the purpose of the model is to predict survival categorizations. By stratifying the data on the survival variable, there exists a similar proportion of each categorization in the training and testing sets which allows for a more effective model.
